Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-10-26 ms.tex
rephrasing a sentence in the appendix

%The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$. 
Where both functions have short-wavelength behavior, we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines. This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$. The matching conditions are
\be
\frac{a_1}{a_2} & = & \frac{ \sin \left( \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} + \frac{\pi}{8} \right) }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }
\\
\frac{a_3}{a_2} & = & \frac{ k_c^{-1/3} }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }.
\ee
By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{tp}$, we find the dispersion relation in Eq. \ref{eq:gamma_nm}.

>>>>

%The discontinuity does not set the value of $a_1$ as that solution does not have a term linear in $\sigma$ when the source is at $\sigma_s=0$. 
When $\sigma_s=0$, we may show that the solutions near and far from $\sigma=0$ have the same approximate form in terms of sines and cosines where both functions have short-wavelength behavior. This matched asymptotic expansion allows us to relate the normalization coefficients $a_1$ and $a_3$. The matching conditions are
\be
\frac{a_1}{a_2} & = & \frac{ \sin \left( \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} + \frac{\pi}{8} \right) }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }
\\
\frac{a_3}{a_2} & = & \frac{ k_c^{-1/3} }{ \sin \left(  \frac{\kappa_n \sigma_{\rm tp} \Delta}{k} - \frac{\pi}{8} \right) }.
\ee
By setting the to denominator of this expression equal to zero and solving it for the eigenfrequency $\gamma_{nm}$ contained in $\sigma_{tp}$, we find the dispersion relation in Eq. \ref{eq:gamma_nm}.
